Assessment of the ability to track changes for nowcasts, measurements, and forecasts

### 2024-04-10 paper.tex
Update on Overleaf.

\abstract{ % Weniger We; Erste zwei Sätze kombinieren
In addition to the numerical precision of measurements, nowcasts, and forecasts,

it can be crucial in applications

it is of interest

how well these reflect changes in the underlying values.
In this article, we focus on the ability to predict the correct direction of changes and refer to it as the ability to track changes. We present visual techniques and quantitative measures to assess this ability and provide extensions for noisy data and estimation uncertainty using bootstrap confidence intervals and exclusion areas.
Three medical or healthcare problems illustrate the assessment: COVID-19-nowcasting, emergency department arrival forecasting, and invasive and non-invasive blood pressure measurements.
}

>>>>

\abstract{ % Weniger We; Erste zwei Sätze kombinieren
In addition to measurements, nowcasts, or forecasts being numerically precise, it is essential how well they reflect changes in the underlying values.
In this article, we focus on predicting the correct direction of changes and refer to it as the ability to track changes.

In this article, we focus on whether they predict the correct direction of changes and refer to it as the ability to track changes.

We present visual techniques and quantitative measures to assess this ability and provide extensions for noisy data and estimation uncertainty using bootstrap confidence intervals and exclusion areas.
Three medical or healthcare problems illustrate the methods: COVID-19-nowcasting, emergency department arrival forecasting, and invasive and non-invasive blood pressure measurements.
}
